A Logistic Regression Approach to CoIL Challenge 2000

### 2019-11-10 final project/Manuscript.tex
Added more lit review to manuscript

\begin{itemize}
\item
  Classification Trees with Bagging (White \& Liu, 2000);
\item
  C4.5 (Seewald, 2000);
\item
  Evolutionary Algorithm (Koudijs, 2000);
\item
  Inductive Learning by Logic Minimization (ILLM) (Gamberger, 2000);
\item
  Mask Perceptron with Boosting (Leckie \& Ferra, 2000);
\item
  Naïve Bayes (Elkan, 2000); and
\item
  Neural Networks(Crocoll, 2000), (Kim \& Street, 2000);
\item
  Scoring System (Lewandowski, 2000);
\item
  Support Vector Machines; and
\item
  XCS (Greenyer, 2000).
\end{itemize}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Crocoll}{}%
Crocoll, W. M. (2000). Artificial neural network portion of coil study. Retrieved from \url{http://www.liacs.nl/~putten/library/cc2000/CROCOL~1.pdf}

@@

@@

@@

@@

@@

\begin{itemize}
\tightlist
\item
  Supplemental tables and/or figures.
\end{itemize}

>>>>

\begin{itemize}
\item
  Classification Trees with Bagging (White \& Liu, 2000);
\item
  C4.5 (Seewald, 2000), (Rickets, 2000);
\item
  Evolutionary Algorithm (Koudijs, 2000);
\item
  Fuzzy Classifier (János Abonyi, 2000);
\item
  Genetic Algorithms and Hill-climbers (Carter, 2000);
\item
  Inductive Learning by Logic Minimization (ILLM) (Gamberger, 2000);
\item
  K-Means (Vesanto \& Sinkkonen, 2000);
\item
  KXEN (Bera \& Lamy, 2000);
\item
  Mask Perceptron with Boosting (Leckie \& Ferra, 2000);
\item
  Midos Algorithm (Krogel, 2000);
\item
  Naïve Bayes (Elkan, 2000); and
\item
  Neural Networks(Crocoll, 2000), (Kim \& Street, 2000);
\item
  Scoring System (Lewandowski, 2000);
\item
  Support Vector Machines; and
\item
  XCS (Greenyer, 2000).
\end{itemize}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Bera}{}%
Bera, M., \& Lamy, B. (2000). Kxen at coil challenge 2000. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/BERAPS~1.pdf}

\leavevmode\hypertarget{ref-Carter}{}%
Carter, J. (2000). Coil 2000 challenge submission: Genetic algorithms and hill-climbers. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/CARTER~1.pdf}

\leavevmode\hypertarget{ref-Crocoll}{}%
Crocoll, W. M. (2000). Artificial neural network portion of coil study. Retrieved from \url{http://www.liacs.nl/~putten/library/cc2000/CROCOL~1.pdf}

@@

\leavevmode\hypertarget{ref-Abonyi}{}%
János Abonyi, H. R. (2000). A simple fuzzy classifier based on inconsistency analysis of labeled data. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/ABONYI~1.pdf}

@@

\leavevmode\hypertarget{ref-Krogel}{}%
Krogel, M.-A. (2000). A data mining case study. Retrieved from \url{http://www.liacs.nl/~putten/library/cc2000/KROGEL~1.pdf}

@@

\leavevmode\hypertarget{ref-Rickets}{}%
Rickets, P. (2000). CoIL challenge 2000 submission. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/RICKET~1.pdf}

@@

\leavevmode\hypertarget{ref-Vesanto}{}%
Vesanto, J., \& Sinkkonen, J. (2000). Submission for the coil challenge 2000. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/VESANT~1.pdf}

@@
